{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-02-07 proposal/thesprop.tex
an actual thesis statemence

\begin{center}
	% TODO: lol
	{\em my research is cool. please let me graduate.}
\end{center}

@@

\begin{itemize}
	\item 2017 January: Submit thesis proposal, submit revised IRB proposal for planned user studies.
	\item 2017 ???uary: Present thesis proposal (whenever the committee is free).
	\item 2017 February-March: Develop ``grading'' TA user study and deploy it in 15-410 (Section~\ref{sec:grading}).
	\item 2017 March-August: Port Landslide to Bochs for use in Pintos OS classes (Section~\ref{sec:pintos-todo}).
	\item 2017 March-August: Implement, evaluate, and write paper about transactional memory project (Section~\ref{sec:tm}).
	\item 2017 August-October: Polish and deploy Pintos user study (Section~\ref{sec:pintos-todo}).
	\item 2017 ???ember: Resubmit paper about 410 user studies (Section~\ref{sec:studence}) (previously rejected from SIGCSE) (whenever an appropriate conference deadline arises.
	\item 2017 October-November: Deploy 410 TA grading study again for more data.
	\item 2017 December: Begin writing thesis.
	\item 2018 January-April: Write thesis. Also fill in miscellaneous gaps, such as the ``variance'' Quicksand experiments (Section~\ref{chap:quicksand}) and measuring Landslide's heuristics' accuracy (Section~\ref{sec:studence}).
	\item 2018 February-March: Deploy Pintos student and 410 TA studies one final time.
	\item 2018 April-May: Defend \& graduate.
\end{itemize}

>>>>

\begin{center}
	{\em Thanks to the new algorithms, heuristics, and concurrency models I have developed,
	stateless model checking is an appropriate and accessible concurrency testing technique
	for programmers in both educational and real-world settings.}
\end{center}

@@

\begin{itemize}
	\item 2017 January: Submit thesis proposal, submit revised IRB proposal for planned user studies.
	\item 2017 ???uary: Present thesis proposal (whenever the committee is free).
	\item 2017 February-March: Develop ``grading'' TA user study and deploy it in 15-410 (Section~\ref{sec:grading}).
	\item 2017 March-August: Port Landslide to Bochs for use in Pintos OS classes (Section~\ref{sec:pintos-todo}).
	\item 2017 March-August: Implement, evaluate, and write paper about transactional memory project (Section~\ref{sec:tm}).
	\item 2017 August-October: Polish and deploy Pintos user study (Section~\ref{sec:pintos-todo}).
	\item 2017 ???ember: Resubmit paper about 410 user studies (Section~\ref{sec:studence}) (previously rejected from SIGCSE) (whenever an appropriate conference deadline arises).
	\item 2017 October-November: Deploy 410 TA grading study again for more data.
	\item 2017 December: Begin writing thesis.
	\item 2018 January-April: Write thesis. Also fill in miscellaneous gaps, such as the ``variance'' Quicksand experiments (Section~\ref{chap:quicksand}) and measuring Landslide's heuristics' accuracy (Section~\ref{sec:studence}).
	\item 2018 February-March: Deploy Pintos student and 410 TA studies one final time.
	\item 2018 April-May: Defend \& graduate.
\end{itemize}
